Enhancing the prediction of sales for newly published books by means of computational intelligence methods

### 2016-04-28 paper.tex
Commenting out comments
References #23. All text-written editorial words are changed to publishing house, and editor is publisher now

\begin{minipage}{2.45in} \begin{verbatim}
reference
author
retail price
subject1
subject2
subject3
editorial
collection
bookbinding
print-run
total sales
dept stores sales
sales through delegates
rest of sales
total sales 1st year
mall sales 1st year
delegates sales 1st year
rest of sales 1st year
total distributed
distributed through dept stores
distributed through delegates
distributed - rest
total distributed 1st year
distrib. through dept stores 1st year
distrib. through delegates 1st year
\end{verbatim} \end{minipage}     &

@@

First, after the editorial company has provided the raw data
(extracted directly from its database), a preprocessing method has
% This should go to the previous section. 
been performed in order to remove incorrect or incoherent patterns,
such as those with null values in required variables, or with negative
sales, for instance. Moreover, the initial set of variables (presented
in Table \ref{tabla:paramsOrig50}) has been reduced by an expert to
use just those that can be known in advance when a new book is
launched, i.e. \textit{pre-sales data}.

@@

Moreover, the application of FS also aims to reduce the computational time for building the forecasting models, along with the complexity of the obtained models themselves. This has been a key factor in this work since one of the objectives is to obtain `easily' interpretable decision models, which can be useful for human experts (editors).

@@

Once the models and results have been obtained for the whole dataset, the same methodology has been applied to some specific cases (editorials) in order to prove the value of the proposal.
Some specific interpretable models have been created as a final result of the work. The aim is that these will cold be used as a decision-aid tool for the experts who have to take decide about the best print-run quantity for new published books, in order to, logically maximise the benefit (or minimise the costs).

@@

\begin{table}
% Shouldn't this table go to "Problem description"? It is a
% preliminary selection - JJ
\caption{Considered pre-sales features and their types. It also shows
  the names of the variables used in the applied methods and if everyone is an input (independent) or an output (dependent) variable.} 
\label{tabla:params_pre_sales}
\begin{center}
\begin{tabular}{|c|l|l|c|c|}
\hline 
No. & Feature Name & Variable & Type & In/Out\\
\hline 
1 & retail price (when launched) & \texttt{ret\_price} & numerical & input\\
2 & main subject (code) & \texttt{subject1} & numerical & input\\
3 &  editorial + collection (joint code) & \texttt{collection} & categorical & input\\
4 & bookbinding (code) & \texttt{binding} & categorical & input\\
5 & gifts (promotional books) & \texttt{gifts} & numerical & input\\
6 & units distributed as novelty & \texttt{distrib\_novelty} & numerical & input\\
7 & total number of points of sale & \texttt{tot\_points\_sale} & numerical & input\\
8 & total number of points of sale (1st year) & \texttt{tot\_points\_sale\_1st\_year} & numerical & input\\
9 & weeks on sale & \texttt{weeks\_sale} & numerical & input\\
10 & print run & \texttt{print\_run} & numerical & input\\
\hline 
\hline
11 & total sales & \texttt{total\_sales} & numerical & output\\
\hline 
\end{tabular}
\end{center}
\end{table}

As it can be seen in the table, \texttt{total\_sales} is the output variable, so it is the objective of the prediction methods. \texttt{print\_run} has been considered as an input variable because it is something to be decided in advance by an editor. In addition, this variable could be interesting to be used to test the prediction model, once it is built. So the editor could try different values for it and see what the predictor yields, in order to take the best decision.

@@

Regarding the feature \textit{editorial}, we have removed it from the final dataset since it is indeed included in the code of \texttt{collection}. In addition, we think it is not really relevant for the accuracy of the models and, moreover, editors will not consider the results in other editorials for predicting its own sales.
% Antonio - Think about this... should we mention this?

Therefore, in order to create simpler and more accurate prediction models, and with the aim to provide them as a useful decision-aid tool for the editor, we have transformed the categorical variable \texttt{subject1} into a numerical one, considering it refers to a code of the Dewey Decimal Classification system for books \footnote{\url{https://en.wikipedia.org/wiki/List_of_Dewey_Decimal_classes}}, and the existing similarity relationship between the books inside a class or subclass. So, for instance, all the books inside subdivisions of class 200, `Religion', are considered as similar regarding their topics, so they could be also close in terms of distance. The same reasoning can be applied to subclasses.

@@

We have analysed the whole dataset (all the editorials), but also performed some experiments considering specific editorials as example cases.
The obtained decision trees have been plotted to show their simplicity and their real value as a decision-aid tool for editors.

@@

\subsection{Results for all editors}
\label{subsec:results_all_editors}

In the first stage of the experiments, forecasting methods have been
applied to the whole dataset. All the pre-sales features have been
considered, including the categorical ones, which make it harder to
process the instances and build the different models. SVM for
instance, must previously transform these categories into binary
variables in order to deal with the data, which means the creation of
a different (and new) variable per each possible value. Thus, in the
case of editorial or collection this would imply the definition of
hundreds of new variables.

Correlation coefficient, error measures and time to build the model have been computed for every method. Obtained results are presented in Table \ref{tab:all_editors_no_fs}.

\begin{table}
\caption{Predicting Total sales for all editors (all the features). 30 repetitions, 10-fold cross validation.
\label{tab:all_editors_no_fs}}
\centering{}%
%{\scriptsize
\begin{tabular}{|c|l|l|l|l|l|l|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
M5P  & 89.0 $\pm$ 0.09  & 214.37 $\pm$ 22.96  & 634.23 $\pm$ 307.76  & 37.46 $\pm$ 3.12  & 48.32 $\pm$ 25.16  & 18.85 $\pm$ 0.61\tabularnewline
\hline 
K-NN  & 78.7 $\pm$ 0.08  & 272.29 $\pm$ 32.38  & 840.59 $\pm$ 240.11  & 47.48 $\pm$ 3.39  & 63.07 $\pm$ 10.29  & 0.001 $\pm$ 0.01\tabularnewline
\hline 
RF & 84.0 $\pm$ 0.05  & 253.37 $\pm$ 29.43  & 788.94 $\pm$ 282.01  & 44.16 $\pm$ 2.76  & 57.77 $\pm$ 8.15  & 4.91 $\pm$ 0.12\tabularnewline
\hline 
LR & 87.2 $\pm$ 0.07  & 308.68 $\pm$ 25.44  & 680.91 $\pm$ 226.41  & 54.05 $\pm$ 4.38  & 52.13 $\pm$ 18.29  & 984.68 $\pm$ 128.21\tabularnewline
\hline 
SVM  & 87.6 $\pm$ 0.04  & 248.76 $\pm$ 27.49  & 732.64 $\pm$ 260.56  & 43.37 $\pm$ 2.35  & 53.47 $\pm$ 6.29  & 6169.24 $\pm$ 281.49\tabularnewline
\hline 
\end{tabular}%}
%}
\end{table}

@@

Moreover, in these experiments it has been seen the difficulty to process 
information related to categorical variables, such as \emph{editorial} and 
\emph{collection}.

@@

Then, the dataset has been projected using SOM, and a visual analysis of the obtained results has been carried out in order to determine the best variables to consider.
An important preprocessing step has been carried out before conducting the SOM analysis, so the two categorical features Editorial and Collection have been
removed from the analysis since SOM cannot deal with them without a previous transformation into numerical ones. However, since they have a large number of unique different values this would be finally impracticable and useless.

@@

Thus, we have run the same experiments as in Section \ref{subsec:results_all_editors} with the whole dataset (all the editors), but considering the selected features by each method. The results are shown in Table

@@

\centering{}%
\caption{Predicting Total sales for all editors based on features selected
by each method.
\label{tab:results_all_editors_fs}}

@@

\section{Experiments of special editorial cases}
\label{example_cases}

This section presents further experiments conducted on data concerning four interesting special editorial cases. These editorials were selected as representative cases which could be very interesting for decision makers and managers in the domain. The four cases are described as follows:

\begin{itemize}
    \item Best seller editorial: this case represents the editorial that sells the highest number of copies regardless the title of the books sold. Therefore, it is an example of a case on a higher business scale.
    \item Medium seller editorial: this represents an editorial that sells medium number of copies compared to the other editorials (Medium business scale). 
    \item Highest variation editorial: this is an example of an editorial that follows a strategy in publishing a very wide range of different titles.
    \item Medium varied editorial: this case represents an editorial that has a median rank between the other editorial regarding the variety of titles sold.
\end{itemize}

Table \ref{Table:special_cases} shows number of sold copies and number of titles published by the selected editorials.

\begin{table}
\caption{Description of editorials considered as special cases.
\label{tab:desc_editorials}}
\centering{}%
\begin{tabular}{|c|l|l|l|}
\hline 
 Case & Different books sold & Total copies sold & Description\\
\hline 
\textit{All editorials} & 6083 & 3201645 & 209 editorials\\
\hline 
\textit{UDL929} & 216 & 460752 & Best selling editorial\\
\hline 
\textit{UDLW12} & 97 & 2635 & Medium selling editorial\\
\hline 
\textit{UDL704} & 293 & 58236 & Editorial with most different\\ 
       &     &       & books sold\\
\hline 
\textit{UDLU11} & 180 & 249481 & Editorial with medium number\\ 
       &     &       &  of different books sold\\
\hline

@@

\begin{table}
\caption{Predicting Total sales for Editorial-UDL929 (The best selling editorial) }
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 90.0 $\pm$0.10 & 670.24 $\pm$181.05  & 1065.34 $\pm$413.84  & 40.83 $\pm$10.86  & 43.56 $\pm$19.87  & 0.03 $\pm$0.002\tabularnewline
\hline 
K-NN  & 73.3 $\pm$0.19  & 1057.21 $\pm$385.04  & 1875.85 $\pm$916.96  & 61.88 $\pm$12.37  & 68.75 $\pm$15.98  & 0 $\pm$0.0001\tabularnewline
\hline 
RF  & 87.6 $\pm$0.11  & 771.83 $\pm$326.34  & 1490.49 $\pm$930.58  & 45.40 $\pm$14.14  & 55.91 $\pm$31.70  & 0.08 $\pm$0.004\tabularnewline
\hline 
LR  & 86.3 $\pm$0.12  & 922.33 $\pm$289.01  & 1399.84 $\pm$619.62  & 56.11 $\pm$16.17  & 56.43 $\pm$25.09  & 0.005 $\pm$0.001\tabularnewline
\hline 
SVM  & 86.7 $\pm$0.1  & 873.22 $\pm$345.16 & 1621.48 $\pm$985.24  & 50.85 $\pm$11.83  & 57.23 $\pm$20.40  & 0.04 $\pm$0.016\tabularnewline
\hline 
\end{tabular}
\label{Table:case1results}
\end{table}

\begin{table}
\caption{Predicting Total sales for Editorial-UDLW12 (The median selling editorial) }
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 83.2 $\pm$0.24  & 14.18 $\pm$6.62  & 23.82 $\pm$11.86  & 43.41 $\pm$20.39  & 55.79 $\pm$30.47  & 0.009 $\pm$0.002\tabularnewline
\hline 
K-NN  & 79.3 $\pm$0.24 & 15.34 $\pm$8.71  & 26.57 $\pm$16.64  & 46.20 $\pm$23.77  & 60.09 $\pm$35.21  & 0.0001 $\pm$0.0002\tabularnewline
\hline 
RF & 85.8 $\pm$0.17  & 14.19 $\pm$6.69  & 23.57 $\pm$11.83  & 42.53 $\pm$16.80  & 53.30 $\pm$23.41  & 0.03 $\pm$0.004\tabularnewline
\hline 
LR  & 82.1 $\pm$0.25 & 14.62 $\pm$7.92  & 24.79 $\pm$15.08  & 44.57 $\pm$24.27  & 56.85 $\pm$35.07  & 0.002 $\pm$0.0005\tabularnewline
\hline 
SVM  & 83.5 $\pm$0.21  & 14.01 $\pm$7.61  & 25.61 $\pm$15.30  & 40.66 $\pm$16.03  & 53.28 $\pm$18.45  & 0.02 $\pm$0.02\tabularnewline
\hline 
\end{tabular}
\label{Table:case2results}
\end{table}

\begin{table}
\caption{Predicting Total sales for Editorial704 (highest number of different titles sold)}
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 &  $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 88.9 $\pm$0.07 & 71.26 $\pm$21.29  & 125.19 $\pm$50.09  & 39.25 $\pm$11.77  & 47.50 $\pm$15.93  & 0.05 $\pm$0.03\tabularnewline
\hline 
K-NN  & 82.6 $\pm$0.10  & 87.60 $\pm$23.21  & 158.63 $\pm$54.16  & 47.62 $\pm$10.32  & 59.17 $\pm$14.43  & 0.0001 $\pm$0.0003\tabularnewline
\hline 
RF & 87.1 $\pm$0.08  & 74.63 $\pm$22.17  & 139.74 $\pm$54.36  & 40.62 $\pm$10.21  & 52.22 $\pm$16.27  & 0.11 $\pm$0.01\tabularnewline
\hline 
LR  & 83.8 $\pm$0.09  & 97.51 $\pm$18.87  & 155.27 $\pm$45.56  & 54.17 $\pm$13.60  & 60.31 $\pm$21.17  & 0.01 $\pm$0.001\tabularnewline
\hline 
SVM  & 87.4 $\pm$0.07  & 78.74 $\pm$22.25  & 147.30 $\pm$57.99  & 42.43 $\pm$7.83  & 53.29 $\pm$9.35  & 0.06 $\pm$0.016\tabularnewline
\hline 
\end{tabular}
\label{Table:case3results}
\end{table}

\begin{table}
\caption{Predicting Total sales for Editorial-UDLU11 (medium number of different books sold))}
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 77.5 $\pm$0.15  & 573.41 $\pm$192.22  & 860.31 $\pm$456.22  & 58.26 $\pm$15.87  & 66.00 $\pm$29.45  & 0.024 $\pm$0.002\tabularnewline
\hline 
K-NN  & 73.2 $\pm$0.16  & 596.62 $\pm$205.37  & 933.06 $\pm$356.11  & 60.62 $\pm$17.85  & 71.36 $\pm$22.34  & 0 $\pm$0.0002\tabularnewline
\hline 
RF & 86.7 $\pm$0.07  & 449.16 $\pm$127.80  & 671.76 $\pm$212.74  & 45.58 $\pm$9.80  & 51.37 $\pm$11.16  & 0.06 $\pm$0.01\tabularnewline
\hline 
LR  & 73.3 $\pm$0.20  & 680.16 $\pm$263.79  & 1103.97 $\pm$850.69  & 69.78 $\pm$27.24  & 86.11 $\pm$71.32  & 0.002 $\pm$0.001\tabularnewline
\hline 
SVM  & 80.4 $\pm$0.12  & 529.35 $\pm$172.50  & 846.01 $\pm$341.12  & 53.26 $\pm$11.92  & 63.54 $\pm$18.25  & 0.03 $\pm$0.02\tabularnewline
\hline 
\end{tabular}
\label{Table:case4results}
\end{table}

@@

Case 1-A: Developing prediction models to predict Total sales for
Editorial704 with ReliefFAttributeEval feature selection.

\begin{table}[!ht]
\caption{Predicting Total sales for Editorial704 (ReliefFAttributeEval-FS) }
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 89.3 $\pm$0.08  & 69.70 $\pm$19.85  & 122.48 $\pm$47.28  & 38.49 $\pm$11.53  & 46.68 $\pm$16.02 & 0.028 $\pm$0.003\tabularnewline
\hline 
K-NN  & 85.6 $\pm$0.10  & 78.39 $\pm$24.12  & 147.07 $\pm$58.02  & 42.58 $\pm$10.99  & 54.42 $\pm$15.54  & 0.0001 $\pm$0.0003\tabularnewline
\hline 
RF & 87.7 $\pm$0.08  & 73.13 $\pm$22.95  & 137.60 $\pm$56.14  & 39.79 $\pm$10.69  & 51.35 $\pm$17.00  & 0.13 $\pm$0.01\tabularnewline
\hline 
LR  & 87.3 $\pm$0.06  & 89.72 $\pm$18.31  & 140.65 $\pm$47.12  & 49.45 $\pm$10.50  & 53.20 $\pm$14.16  & 0.0008 $\pm$0.0005\tabularnewline
\hline 
SVM  & 87.7 $\pm$0.07  & 77.30 $\pm$22.25  & 146.46 $\pm$57.68  & 41.67 $\pm$7.99  & 53.10 $\pm$9.51  & 0.05 $\pm$0.02\tabularnewline
\hline 
\end{tabular}
\end{table}

Case 1-B: Developing prediction models to predict Total sales for
Editorial-UDLU11 with ReliefFAttributeEval feature selection

\begin{table}[!ht]
\caption{Predicting Total sales for Editorial-UDLU11 (ReliefFAttributeEval-FS)}

@@

Case 2-A: Developing prediction models to predict Total sales for
Editorial-UDL929 with ReliefFAttributeEval feature selection.

>>>>

\begin{minipage}{2.45in} \begin{verbatim}
reference
author
retail price
subject1
subject2
subject3
publisher
collection
bookbinding
print-run
total sales
dept stores sales
sales through delegates
rest of sales
total sales 1st year
mall sales 1st year
delegates sales 1st year
rest of sales 1st year
total distributed
distributed through dept stores
distributed through delegates
distributed - rest
total distributed 1st year
distrib. through dept stores 1st year
distrib. through delegates 1st year
\end{verbatim} \end{minipage}     &

@@

First, after the publishing house has provided the raw data
(extracted directly from its database), a preprocessing method has
% This should go to the previous section. 
been performed in order to remove incorrect or incoherent patterns,
such as those with null values in required variables, or with negative
sales, for instance. Moreover, the initial set of variables (presented
in Table \ref{tabla:paramsOrig50}) has been reduced by an expert to
use just those that can be known in advance when a new book is
launched, i.e. \textit{pre-sales data}.

@@

Moreover, the application of FS also aims to reduce the computational time for building the forecasting models, along with the complexity of the obtained models themselves. This has been a key factor in this work since one of the objectives is to obtain `easily' interpretable decision models, which can be useful for human experts (publishers).

@@

Once the models and results have been obtained for the whole dataset, the same methodology has been applied to some specific cases (publishing houses) in order to prove the value of the proposal.
Some specific interpretable models have been created as a final result of the work. The aim is that these will cold be used as a decision-aid tool for the experts who have to take decide about the best print-run quantity for new published books, in order to, logically maximise the benefit (or minimise the costs).

@@

\begin{table}
% Shouldn't this table go to "Problem description"? It is a
% preliminary selection - JJ
\caption{Considered pre-sales features and their types. It also shows
  the names of the variables used in the applied methods and if everyone is an input (independent) or an output (dependent) variable.} 
\label{tabla:params_pre_sales}
\begin{center}
\begin{tabular}{|c|l|l|c|c|}
\hline 
No. & Feature Name & Variable & Type & In/Out\\
\hline 
1 & retail price (when launched) & \texttt{ret\_price} & numerical & input\\
2 & main subject (code) & \texttt{subject1} & numerical & input\\
3 &  publisher + collection (joint code) & \texttt{collection} & categorical & input\\
4 & bookbinding (code) & \texttt{binding} & categorical & input\\
5 & gifts (promotional books) & \texttt{gifts} & numerical & input\\
6 & units distributed as novelty & \texttt{distrib\_novelty} & numerical & input\\
7 & total number of points of sale & \texttt{tot\_points\_sale} & numerical & input\\
8 & total number of points of sale (1st year) & \texttt{tot\_points\_sale\_1st\_year} & numerical & input\\
9 & weeks on sale & \texttt{weeks\_sale} & numerical & input\\
10 & print run & \texttt{print\_run} & numerical & input\\
\hline 
\hline
11 & total sales & \texttt{total\_sales} & numerical & output\\
\hline 
\end{tabular}
\end{center}
\end{table}

As it can be seen in the table, \texttt{total\_sales} is the output variable, so it is the objective of the prediction methods. \texttt{print\_run} has been considered as an input variable because it is something to be decided in advance by a publisher. In addition, this variable could be interesting to be used to test the prediction model, once it is built. So the publisher could try different values for it and see what the predictor yields, in order to take the best decision.

@@

Regarding the feature \textit{publisher}, we have removed it from the final dataset since it is indeed included in the code of \texttt{collection}. In addition, we think it is not really relevant for the accuracy of the models and, moreover, publishers will not consider the results in other publishing houses for predicting its own sales.
% Antonio - Think about this... should we mention this?

Therefore, in order to create simpler and more accurate prediction models, and with the aim to provide them as a useful decision-aid tool for the publisher, we have transformed the categorical variable \texttt{subject1} into a numerical one, considering it refers to a code of the Dewey Decimal Classification system for books \footnote{\url{https://en.wikipedia.org/wiki/List_of_Dewey_Decimal_classes}}, and the existing similarity relationship between the books inside a class or subclass. So, for instance, all the books inside subdivisions of class 200, `Religion', are considered as similar regarding their topics, so they could be also close in terms of distance. The same reasoning can be applied to subclasses.

@@

We have analysed the whole dataset (all the publishing houses), but also performed some experiments considering specific publishing houses as example cases.
The obtained decision trees have been plotted to show their simplicity and their real value as a decision-aid tool for publishers.

@@

\subsection{Results for all publishers}
\label{subsec:results_all_publishers}

In the first stage of the experiments, forecasting methods have been
applied to the whole dataset. All the pre-sales features have been
considered, including the categorical ones, which make it harder to
process the instances and build the different models. SVM for
instance, must previously transform these categories into binary
variables in order to deal with the data, which means the creation of
a different (and new) variable per each possible value. Thus, in the
case of \emph{publisher} or \emph{collection} this would imply the definition of
hundreds of new variables.

Correlation coefficient, error measures and time to build the model have been computed for every method. Obtained results are presented in Table \ref{tab:all_publishers_no_fs}.

\begin{table}
\caption{Predicting Total sales for all publishers (all the features). 30 repetitions, 10-fold cross validation.
\label{tab:all_publishers_no_fs}}
\centering{}%
%{\scriptsize
\begin{tabular}{|c|l|l|l|l|l|l|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
M5P  & 89.0 $\pm$ 0.09  & 214.37 $\pm$ 22.96  & 634.23 $\pm$ 307.76  & 37.46 $\pm$ 3.12  & 48.32 $\pm$ 25.16  & 18.85 $\pm$ 0.61\tabularnewline
\hline 
K-NN  & 78.7 $\pm$ 0.08  & 272.29 $\pm$ 32.38  & 840.59 $\pm$ 240.11  & 47.48 $\pm$ 3.39  & 63.07 $\pm$ 10.29  & 0.001 $\pm$ 0.01\tabularnewline
\hline 
RF & 84.0 $\pm$ 0.05  & 253.37 $\pm$ 29.43  & 788.94 $\pm$ 282.01  & 44.16 $\pm$ 2.76  & 57.77 $\pm$ 8.15  & 4.91 $\pm$ 0.12\tabularnewline
\hline 
LR & 87.2 $\pm$ 0.07  & 308.68 $\pm$ 25.44  & 680.91 $\pm$ 226.41  & 54.05 $\pm$ 4.38  & 52.13 $\pm$ 18.29  & 984.68 $\pm$ 128.21\tabularnewline
\hline 
SVM  & 87.6 $\pm$ 0.04  & 248.76 $\pm$ 27.49  & 732.64 $\pm$ 260.56  & 43.37 $\pm$ 2.35  & 53.47 $\pm$ 6.29  & 6169.24 $\pm$ 281.49\tabularnewline
\hline 
\end{tabular}%}
%}
\end{table}

@@

Moreover, in these experiments it has been seen the difficulty to process 
information related to categorical variables, such as \emph{publisher} and 
\emph{collection}.

@@

Then, the dataset has been projected using SOM, and a visual analysis of the obtained results has been carried out in order to determine the best variables to consider.
An important preprocessing step has been carried out before conducting the SOM analysis, so the two categorical features \emph{publisher} and \emph{collection} have been
removed from the analysis since SOM cannot deal with them without a previous transformation into numerical ones. However, since they have a large number of unique different values this would be finally impracticable and useless.

@@

Thus, we have run the same experiments as in Section \ref{subsec:results_all_publishers} with the whole dataset (all the publishers), but considering the selected features by each method. The results are shown in Table

@@

\centering{}%
\caption{Predicting Total sales for all publishers based on features selected
by each method.
\label{tab:results_all_publishers_fs}}

@@

\section{Experiments of special publishing houses cases}
\label{example_cases}

This section presents further experiments conducted on data concerning four interesting special publishing house cases. These publishing houses were selected as representative cases which could be very interesting for decision makers and managers in the domain. The four cases are described as follows:

\begin{itemize}
    \item Best seller publishing house: this case represents the publishing house that sells the highest number of copies regardless the title of the books sold. Therefore, it is an example of a case on a higher business scale.
    \item Medium seller publishing house: this represents an publishing house that sells medium number of copies compared to the other publishing houses (Medium business scale). 
    \item Highest variation publishing house: this is an example of an publishing house that follows a strategy in publishing a very wide range of different titles.
    \item Medium varied publishing house: this case represents an publishing house that has a median rank between the other publishing house regarding the variety of titles sold.
\end{itemize}

Table \ref{Table:special_cases} shows number of sold copies and number of titles published by the selected publishing houses.

\begin{table}
\caption{Description of publishing houses considered as special cases.
\label{tab:desc_publishing houses}}
\centering{}%
\begin{tabular}{|c|l|l|l|}
\hline 
 Case & Different books sold & Total copies sold & Description\\
\hline 
\textit{All publishing houses} & 6083 & 3201645 & 209 publishing houses\\
\hline 
\textit{UDL929} & 216 & 460752 & Best selling publishing house\\
\hline 
\textit{UDLW12} & 97 & 2635 & Medium selling publishing house\\
\hline 
\textit{UDL704} & 293 & 58236 & Publishing house with most different\\ 
       &     &       & books sold\\
\hline 
\textit{UDLU11} & 180 & 249481 & Publishing house with medium number\\ 
       &     &       &  of different books sold\\
\hline

@@

\begin{table}
\caption{Predicting Total sales for PublishingHouse-UDL929 (The best selling publishing house) }
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 90.0 $\pm$0.10 & 670.24 $\pm$181.05  & 1065.34 $\pm$413.84  & 40.83 $\pm$10.86  & 43.56 $\pm$19.87  & 0.03 $\pm$0.002\tabularnewline
\hline 
K-NN  & 73.3 $\pm$0.19  & 1057.21 $\pm$385.04  & 1875.85 $\pm$916.96  & 61.88 $\pm$12.37  & 68.75 $\pm$15.98  & 0 $\pm$0.0001\tabularnewline
\hline 
RF  & 87.6 $\pm$0.11  & 771.83 $\pm$326.34  & 1490.49 $\pm$930.58  & 45.40 $\pm$14.14  & 55.91 $\pm$31.70  & 0.08 $\pm$0.004\tabularnewline
\hline 
LR  & 86.3 $\pm$0.12  & 922.33 $\pm$289.01  & 1399.84 $\pm$619.62  & 56.11 $\pm$16.17  & 56.43 $\pm$25.09  & 0.005 $\pm$0.001\tabularnewline
\hline 
SVM  & 86.7 $\pm$0.1  & 873.22 $\pm$345.16 & 1621.48 $\pm$985.24  & 50.85 $\pm$11.83  & 57.23 $\pm$20.40  & 0.04 $\pm$0.016\tabularnewline
\hline 
\end{tabular}
\label{Table:case1results}
\end{table}

\begin{table}
\caption{Predicting Total sales for PublishingHouse-UDLW12 (The median selling publishing house) }
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 83.2 $\pm$0.24  & 14.18 $\pm$6.62  & 23.82 $\pm$11.86  & 43.41 $\pm$20.39  & 55.79 $\pm$30.47  & 0.009 $\pm$0.002\tabularnewline
\hline 
K-NN  & 79.3 $\pm$0.24 & 15.34 $\pm$8.71  & 26.57 $\pm$16.64  & 46.20 $\pm$23.77  & 60.09 $\pm$35.21  & 0.0001 $\pm$0.0002\tabularnewline
\hline 
RF & 85.8 $\pm$0.17  & 14.19 $\pm$6.69  & 23.57 $\pm$11.83  & 42.53 $\pm$16.80  & 53.30 $\pm$23.41  & 0.03 $\pm$0.004\tabularnewline
\hline 
LR  & 82.1 $\pm$0.25 & 14.62 $\pm$7.92  & 24.79 $\pm$15.08  & 44.57 $\pm$24.27  & 56.85 $\pm$35.07  & 0.002 $\pm$0.0005\tabularnewline
\hline 
SVM  & 83.5 $\pm$0.21  & 14.01 $\pm$7.61  & 25.61 $\pm$15.30  & 40.66 $\pm$16.03  & 53.28 $\pm$18.45  & 0.02 $\pm$0.02\tabularnewline
\hline 
\end{tabular}
\label{Table:case2results}
\end{table}

\begin{table}
\caption{Predicting Total sales for PublishingHouse704 (highest number of different titles sold)}
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 &  $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 88.9 $\pm$0.07 & 71.26 $\pm$21.29  & 125.19 $\pm$50.09  & 39.25 $\pm$11.77  & 47.50 $\pm$15.93  & 0.05 $\pm$0.03\tabularnewline
\hline 
K-NN  & 82.6 $\pm$0.10  & 87.60 $\pm$23.21  & 158.63 $\pm$54.16  & 47.62 $\pm$10.32  & 59.17 $\pm$14.43  & 0.0001 $\pm$0.0003\tabularnewline
\hline 
RF & 87.1 $\pm$0.08  & 74.63 $\pm$22.17  & 139.74 $\pm$54.36  & 40.62 $\pm$10.21  & 52.22 $\pm$16.27  & 0.11 $\pm$0.01\tabularnewline
\hline 
LR  & 83.8 $\pm$0.09  & 97.51 $\pm$18.87  & 155.27 $\pm$45.56  & 54.17 $\pm$13.60  & 60.31 $\pm$21.17  & 0.01 $\pm$0.001\tabularnewline
\hline 
SVM  & 87.4 $\pm$0.07  & 78.74 $\pm$22.25  & 147.30 $\pm$57.99  & 42.43 $\pm$7.83  & 53.29 $\pm$9.35  & 0.06 $\pm$0.016\tabularnewline
\hline 
\end{tabular}
\label{Table:case3results}
\end{table}

\begin{table}
\caption{Predicting Total sales for PublishingHouse-UDLU11 (medium number of different books sold))}
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 77.5 $\pm$0.15  & 573.41 $\pm$192.22  & 860.31 $\pm$456.22  & 58.26 $\pm$15.87  & 66.00 $\pm$29.45  & 0.024 $\pm$0.002\tabularnewline
\hline 
K-NN  & 73.2 $\pm$0.16  & 596.62 $\pm$205.37  & 933.06 $\pm$356.11  & 60.62 $\pm$17.85  & 71.36 $\pm$22.34  & 0 $\pm$0.0002\tabularnewline
\hline 
RF & 86.7 $\pm$0.07  & 449.16 $\pm$127.80  & 671.76 $\pm$212.74  & 45.58 $\pm$9.80  & 51.37 $\pm$11.16  & 0.06 $\pm$0.01\tabularnewline
\hline 
LR  & 73.3 $\pm$0.20  & 680.16 $\pm$263.79  & 1103.97 $\pm$850.69  & 69.78 $\pm$27.24  & 86.11 $\pm$71.32  & 0.002 $\pm$0.001\tabularnewline
\hline 
SVM  & 80.4 $\pm$0.12  & 529.35 $\pm$172.50  & 846.01 $\pm$341.12  & 53.26 $\pm$11.92  & 63.54 $\pm$18.25  & 0.03 $\pm$0.02\tabularnewline
\hline 
\end{tabular}
\label{Table:case4results}
\end{table}

@@

Case 1-A: Developing prediction models to predict Total sales for
PublishingHouse704 with ReliefFAttributeEval feature selection.

\begin{table}[!ht]
\caption{Predicting Total sales for PublishingHouse704 (ReliefFAttributeEval-FS) }
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 89.3 $\pm$0.08  & 69.70 $\pm$19.85  & 122.48 $\pm$47.28  & 38.49 $\pm$11.53  & 46.68 $\pm$16.02 & 0.028 $\pm$0.003\tabularnewline
\hline 
K-NN  & 85.6 $\pm$0.10  & 78.39 $\pm$24.12  & 147.07 $\pm$58.02  & 42.58 $\pm$10.99  & 54.42 $\pm$15.54  & 0.0001 $\pm$0.0003\tabularnewline
\hline 
RF & 87.7 $\pm$0.08  & 73.13 $\pm$22.95  & 137.60 $\pm$56.14  & 39.79 $\pm$10.69  & 51.35 $\pm$17.00  & 0.13 $\pm$0.01\tabularnewline
\hline 
LR  & 87.3 $\pm$0.06  & 89.72 $\pm$18.31  & 140.65 $\pm$47.12  & 49.45 $\pm$10.50  & 53.20 $\pm$14.16  & 0.0008 $\pm$0.0005\tabularnewline
\hline 
SVM  & 87.7 $\pm$0.07  & 77.30 $\pm$22.25  & 146.46 $\pm$57.68  & 41.67 $\pm$7.99  & 53.10 $\pm$9.51  & 0.05 $\pm$0.02\tabularnewline
\hline 
\end{tabular}
\end{table}

Case 1-B: Developing prediction models to predict Total sales for
PublishingHouse-UDLU11 with ReliefFAttributeEval feature selection

\begin{table}[!ht]
\caption{Predicting Total sales for PublishingHouse-UDLU11 (ReliefFAttributeEval-FS)}

@@

Case 2-A: Developing prediction models to predict Total sales for
PublishingHouse-UDL929 with ReliefFAttributeEval feature selection.
